Our Title

### 2015-05-01 draft.tex
Added in update to "Global Relationships" section, and some more weapon info. Added an Appendix for nuclear terminology.

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\input{ix-utf8enc.dfu}
\usepackage{graphicx}
% \usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

@@

@@

@@

2.1.2 Critical Mass

@@

@@

\subsubsection{RDD Case Study}

@@

% \begin{itemize}
%   \item \ce{^{60}Co}
%   \item \ce{^{3}H}  
%   \item \ce{^{90}Sr}
%   \item \ce{^{131}I}
%   \item \ce{^{137}Cs}
%   \item \ce{^{192}Ir}
%   \item \ce{^{241}Am} \footnote{Radioisotope undergoes decay through a chain of isotopes, including additional types of radiation emissions (e.g., combination of primary beta and secondary gamma emissions)} 
%   \item \ce{^{238}Pu} \footnotemark[2] \footnote{Not included in this assessment due to higher level of radiological materials controls classifications for plutonium materials (e.g., HLW).} \footnote{Relative abundance or material availability is very low.}
%   \item \ce{^{210}Po} \footnotemark[2] \footnotemark[4] \footnote{From this listing, it is possible that polonium-210 does not pose a significant threat.[3] MAKE THIS ITS OWN REFERENCE -> Additional details are provided by the CDC on polonium: http://www.bt.cdc.gov/radiation/isotopes/polonium/qa.asp.}
%   \item \ce{^{252}Cf} \footnotemark[2] \footnotemark[4]
% 
% \end{itemize}

@@

There are two main designs for fission weapons:  gun-type and  implosion-type. Implosion-type weapons can be fueled with either uranium or plutonium; however,  gun-type weapons can only use uranium fuel, as the high spontaneous fission rate of  plutonium would have a high probability of a fizzle yield. While both designs produce functional weapons, an implosion device is significantly more difficult to design. If ISIL were to obtain a fission device through an indigenous program, it is extremely unlikely such a device would use plutonium. However, it would be possible for them to steal or purchase a completed plutonium physics package, thus making it necessary to monitor for such a device \cite{Moody2014}.

@@

\subsubsection{?????????   Missing   ???????????}

@@

\appendix
\chapter[Appendix A: Intelligence Overview]{Intelligence Overview}  \label{app:intel}

@@

\chapter[Appendix B: International Partnerships]{International Partnerships} \label{app:partners}

>>>>

\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\input{ix-utf8enc.dfu}
\usepackage{graphicx}
% \usepackage{svg}

% \usepackage[colorinlistoftodos]{todonotes}
\usepackage{float}
\usepackage{multirow}
\usepackage[table,xcdraw]{xcolor}

@@

Finally, it is important to consider the non-organizationally alligned support that ISIS recieves in the form of foriegn fighters.  The flow of these foriegn fighters has dwarfed the influx associated with previous calls to Jihad, such as Afghanistan in the 1980s \cite{Barrett2014}.  These fighters come from all over the world as shown in \autoref{fig:enablers}, and they bring a diverse background and skill set with them.  Although no comprehensive list has been established in the open literature about the skills brought to ISIL via foreign fighters, it is likely that some of the foreign fighters possess skills necessarily to develop, fabricate, and assemble components of a nuclear weapon.

\begin{figure}[h]
 \centering
 \includegraphics[scale=0.6]{./figures/enablers.jpg}
   \caption{Flow of foreign fighters into Syria \cite{Thorp2014}. }
     \label{fig:enablers}
\end{figure}

@@

A glossary of much of the nuclear-related terminology used in this paper may be found summarized in  \autoref{app:glossary}.

@@

\subsection{???????  Needs content proofing   ????????}

\subsection{???????   Need discussion of criticality  ??????}

A fission device operates on the principle that fissile materials (list of materials) will undergo fission when stuck by neutrons of sufficient kinetic energy. A nuclide which undergoes fission will release between 100-200 MeV in addition to 2-3 neutrons, which may be utilized to cause subsequent fissions in other fissile nuclei \cite{krane1987introductory}. The minimum amount of fissile material needed in order to sustain a chain reaction is known as the critical mass, which depends on the type, density, and shape of material used. A tamper, which is a high Z material which acts as a neutron reflector, is typically used in order to reduce the critical mass.

\subsection{Critical Mass}

@@

\subsection{???????? Scott's added brief RDD info, needs content proofing. Andrew tried to use it to link the above section to the case study    ?????????}

The effect of such a device will depend on the type of radioactive material used and the method of dispersion. The radioactive material may be an alpha, beta, or gamma emitter, or any combination therein (see \autoref{app:glossary} for definitions of radiation). The health impact of the dose received from all radiation sources will be a function of the concentration of the radionuclides in the environment and the duration of exposure. Based on the case study presented in \autoref{sec:case_study}, it is unlikely that many individuals would die from acute exposure to radiation; the conventional explosives used in the RDD are expected to cause the greatest immediate damage \cite{USDepartmentofHealthandHumanServices:RadiationEmergencyMedicalManagement2014}.

@@

\subsubsection{RDD Case Study}  \label{sec:case_study}

@@

% \begin{itemize}
%   \item \ce{^{60}Co}
%   \item \ce{^{3}H}  
%   \item \ce{^{90}Sr}
%   \item \ce{^{131}I}
%   \item \ce{^{137}Cs}
%   \item \ce{^{192}Ir}
%   \item \ce{^{241}Am} \footnote{Radioisotope undergoes decay through a chain of isotopes, including additional types of radiation emissions (e.g., combination of primary beta and secondary gamma emissions)} 
%   \item \ce{^{238}Pu} \footnotemark[2] \footnote{Not included in this assessment due to higher level of radiological materials controls classifications for plutonium materials (e.g., HLW).} \footnote{Relative abundance or material availability is very low.}
%   \item \ce{^{210}Po} \footnotemark[2] \footnotemark[4] \footnote{From this listing, it is possible that polonium-210 does not pose a significant threat.[3]  Additional details are provided by the CDC on polonium \cite{CentersforDiseaseControlandPrevention2014}}
%   \item \ce{^{252}Cf} \footnotemark[2] \footnotemark[4]
% 
% \end{itemize}

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{./figures/assembly_methods.pdf}
  \caption{Schematic illustrations of gun-type and implosion devices \cite{WikimediaCommons2006}.}
  \label{fig:assembly_methods}
\end{figure}

There are two main designs for fission weapons:  gun-type and  implosion-type. Both of these designs (seen schematically in \autoref{fig:assembly_methods}) combine previously subcritical assemblies of SNM in order to form a critical assembly, initiating a nuclear explosion \cite{Serber1992}. Implosion-type weapons can be fueled with either uranium or plutonium; however,  gun-type weapons can only use uranium fuel, as the high spontaneous fission rate of  plutonium would have a high probability of a fizzle yield. While both designs produce functional weapons, an implosion device is significantly more difficult to design, requiring advanced detonation and timing circuits \cite{Serber1992}. If ISIL were to obtain a fission device through an indigenous program, it is extremely unlikely such a device would use plutonium. However, it would be possible for them to steal or purchase a completed plutonium physics package, or divert the technology to trigger an implosion device from another nuclear-capable state, thus making it necessary to monitor for such a device \cite{Moody2014}.

@@

\subsubsection{?????? Scott's Brief Fusion Summary, needs  proofing}

A fusion device is a multistage weapon which consists of multiple fission stages and at least one fusion stage. The fission stages are used to drive the fusion reaction, which in turn provides a short, high energy pulse of neutrons which then drive additional fission. This complicated array of triggering devices is used in order to explosive yields which far exceed a single fission device. \autoref{fig:ulam_device} shows an example of a fusion device.

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.45]{./figures/Ulam_device.png}
  \caption{Schematic representation of the design of a fusion weapon \cite{WikimediaCommons2005}.}
  \label{fig:ulam_device}
\end{figure}

The basic process of detonation is as follows: The primary device triggers first and supplies x-rays, which heat the secondary device, which heats the polystyrene foam into a plasma. The Plutonium “spark plug” at the center of the fusion assembly begins to undergo fission due to the compression from the polystyrene plasma. The Lithium-6 deuteride blanket, which surrounds the plutonium spark plug, produces tritium and begins the fusion stage. The flux of neutrons from the fusion reactions causes the \ce{^{238}U} tamper to undergo fission. At this stage the device breaks apart and a detonation is complete \cite{Defense1998}.

Fusion weapons are far more sophisticated than fission weapons, and essentially consists of three fission devices and one fusion device. It is assumed that ISIL is pursuing nuclear weapons in order to commit acts of terrorism; optimizing yield does not greatly enhance the terror of a nuclear device. Due to the complexity of the design of multistage fusion devices, it is assumed that ISIL will elect to pursue gun-type fission weapons.

@@

\appendix
\chapter[Appendix A: Glossary of Nuclear Terminology]{Glossary of Nuclear Terminology}  \label{app:glossary}

\textit{Note: All terminology is taken from the U.S. Nuclear Regulatory Commission  \cite{USNRC2015}.}

Radioactive Decay: The spontaneous transformation of one radioisotope into one or more different isotopes. The isotopes created may or may not also be radioactive. Radioactive decay may also be used to refer to the emission of a gamma ray or a conversion electron emission, which reduces the energy of the decaying isotope but does not change its identity.

Alpha Radiation: The radioactive decay of a nuclide which results in the emission of a 4-Helium atom. Alpha radiation is sometimes followed by gamma emission.

Beta Radiation: A radioactive decay of a nuclide which results in the emission of an electron and an electron antineutrino pair, or a positron and an electron neutrino pair.

Fusion: A nuclear reaction in which atomic nuclei of low atomic number merge and become a heavier nucleus, thereby releasing energy.

Special Nuclear Material: Plutonium, 233-Uranium, Uranium with enrichments of 233-Uranium or 235-Uranium.

Gamma Radiation: A radioactive decay which results in the emission of a high energy- short-wavelength, electromagnetic radiation emitted from within the nucleus of an atom. Gamma radiation often follows the emission of an alpha or beta particle, and always follows a fission event.

Electron Volt: A unit of energy equivalent to the work required to accelerate an electron through a potential difference of 1 volt.

Fission: The splitting of an atom, which releases energy. During fission, a heavy (large A) nucleus splits into two or three smaller nuclei and emits gamma rays and neutrons.

Nuclide: A distinct nucleus, defined by the total number of neutrons and protons contained therein.

Fast Neutron: A neutron with kinetic energy in excess of 1.5 MeV.

Thermal Neutron: A neutron which is in thermal equilibrium with its surroundings.

Fissile Material: A nuclide that is capable of undergoing fission after capturing thermal neutrons.

Fissionable Material: A nuclide that is capable of undergoing fission after capturing a fast or thermal neutron.

% \appendix
\chapter[Appendix B: Intelligence Overview]{Intelligence Overview}  \label{app:intel}

@@

\chapter[Appendix C: International Partnerships]{International Partnerships} \label{app:partners}
